---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(basf)
```


# basf

The goal of basf is to smooth over some of the peculiarities of the sf package, with a very short list of features. 

- plot simple features in a base graphics way that sp did. 
- read vector data with a straightforward extent filter

## Installation

From CRAN in the usual way. 

```{r cran, eval=FALSE}
install.packages("basf")
```

From Github: 

```{r install, eval=FALSE}
#install.packages("remotes")
remotes::install_github("mdsumner/basf")
```

Use `library(basf)` instead of `library(sf)` if you want these features. 

## Plotting 


There will be a warning when basf starts up because this is what it does. 

```R
Registered S3 method overwritten by 'basf':
  method  from
  plot.sf sf  
```

This example shows the impact of basf on plotting.

```{r example}
library(basf)

## all the stuff is available
x <- read_sf(system.file("shape/nc.shp", package="sf"))

## all we've changed is the plot command
plot(x)
plot(x[sample(1:nrow(x), 10), ], col = rainbow(10), add = TRUE)
## overplotting works
axis(1); axis(2)
abline(v = -80, h = -34)
```

Without basf, we would have to do extra format-aware workarounds when setting up
the plot. I find this incredibly disruptive, perhaps because I've used R and sp
for so long - I use plotting every day to verify my work. It makes no sense to
me to make things format-specific so I'm kind of mystified as to why it's gone
this way.

```R
library(sf)
x <- read_sf(system.file("shape/nc.shp", package="sf"))

plot(x[1], reset = FALSE, col = NA, main = "")
plot(x[sample(1:nrow(x), 10), ], col = rainbow(10), add = TRUE)
axis(1); axis(2)
abline(v = -80, h = -34)
```

## Reading

This example shows the impact of basf on reading.  We would otherwise obtain 32 polygons from this file. 

The second optional argument `ext` can be an extent, either a raw vector xmin,xmax,ymin,ymax as here or a spatial object. 

```R
library(basf)
read_ext("../measoshapes/inst/extdata/measo_regions_ll.gpkg", c(100, 120, -80, -10))
Simple feature collection with 8 features and 3 fields
geometry type:  POLYGON
dimension:      XY
bbox:           xmin: 30 ymin: -80 xmax: 170 ymax: -30
geographic CRS: WGS 84
```

---

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/mdsumner/basf/blob/master/CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.

