---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/mdsumner/basf?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/basf)
  
# basf

The goal of basf is to plot simple features in a base graphics way that sp did. 

## Installation

```{r install, eval=FALSE}
devtools::install_github("mdsumner/basf")
```

The idea is to use `library(basf)` instead of `library(sf)` and get on with the job. 


## Example

There will be a warning when basf starts up because this is what it does. 

```R
Registered S3 method overwritten by 'basf':
  method  from
  plot.sf sf  
```

This is a basic example which shows the only impact of basf.

```{r example}
library(basf)

## all the stuff is available
x <- read_sf(system.file("shape/nc.shp", package="sf"))

## all we've changed is the plot command
plot(x)
plot(x[sample(1:nrow(x), 10), ], col = rainbow(10), add = TRUE)
## overplotting works
axis(1); axis(2)
abline(v = -80, h = -34)
```

Without basf, we would have to do extra format-aware workarounds when setting
up the plot. 

```R
library(sf)
x <- read_sf(system.file("shape/nc.shp", package="sf"))

plot(x[1], reset = FALSE, col = NA, main = "")
plot(x[sample(1:nrow(x), 10), ], col = rainbow(10), add = TRUE)
axis(1); axis(2)
abline(v = -80, h = -34)
```

---

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/mdsumner/basf/blob/master/CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.

