---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# basf

The goal of basf is to plot simple features in a base graphics way. 

This is for developers writing packages frustrated with the way sf plots
and the ongoing disruptions. It's not for general use. 

## Installation

```{r install, eval=FALSE}
devtools::install_github("mdsumner/basf")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(basf)
## all the stuff is available
nc <- read_sf(system.file("shape/nc.shp", package="sf"))

## all we've changed is the plot command
plot(nc)
plot(nc[sample(1:nrow(nc), 10), ], col = rainbow(10), add = TRUE)
```



Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.

